---
title: "Employee Atrrition graphs_DH"
output: html_document
---

```{r}
library(tidyverse)
library(readr)
library(ggplot2)
```

# loading the data
```{r}
# df.csv is the data before special preparations for machine learning, e.g., categorical variables converted to dummy variables.
df <- read_csv("HR_Employee_Attrition.csv")


# This is the data frame that contains the predictions.
out <- read_csv("out.csv")

colnames(out)[colnames(out) == 'X1'] <- 'EmployeeNumber'
```


```{r}
# Historic will be the data frame we use to create the graphs comparing quitters with non-quitters.
historic = df %>% filter(!EmployeeNumber %in% out$EmployeeNumber)

# Current is data about ostensibly current employees.
# We don't need df's Attrition in the current dataframe. 
current = subset(df, select=-Attrition) %>% filter(EmployeeNumber %in% out$EmployeeNumber)
                          #^^^^^^^^^^^^^^^^^^
                    #  This is simply a list of 
                    # the current employees' 
                    # EmployeeNumbers
current = merge(out[, c("EmployeeNumber", "Name", "Attrition")], current, by="EmployeeNumber")

# write dataframes to csv
write.csv(current, "current.csv", row.names = FALSE)
write.csv(historic, "historic.csv", row.names = FALSE)
```



# Here I'm creating plots for the historic variables. The purpose of this is to see how, broadly speaking, quitters differ from non-quitters.

# Age
```{r}
dataset = historic

library(ggplot2)
age_graph = ggplot(data=dataset, aes(x=Attrition, y=Age, fill=Attrition))+
  geom_boxplot(notch=TRUE, outlier.alpha = 0)+
  theme_minimal()
# Notches are used to compare groups; if the notches of two boxes do not overlap, this is a strong evidence that the medians differ.
age_graph
```

# BusinessTravel graph
# categorical variable: should categories be sorted, and should attrition be redone as boolean?
```{r}
library(ggplot2)
businesstravel_graph = ggplot(data=dataset, aes(x=BusinessTravel,  fill=Attrition))+
  geom_bar(position = "fill")+
  theme_minimal()

businesstravel_graph
```

# HourlyRate graph
```{r}
library(ggplot2)
hourlyrate_graph = ggplot(data=dataset, aes(x=Attrition, y=HourlyRate, fill=Attrition, group=Attrition))+
  geom_boxplot(notch=TRUE, outlier.alpha = 0)+
  theme_minimal()
# Notches are used to compare groups; if the notches of two boxes do not overlap, this is a strong evidence that the medians differ.
hourlyrate_graph
```
# Department Graph

```{r}
library(ggplot2)
department_graph = ggplot(data=dataset, aes(x=Department,  fill=Attrition))+
  geom_bar(position = "fill")+
  theme_minimal()
# Notches are used to compare groups; if the notches of two boxes do not overlap, this is a strong evidence that the medians differ.
department_graph
```

# Education Graph
```{r}
library(ggplot2)
education_graph = ggplot(data=dataset, aes(x=Education,  fill=Attrition))+
  geom_bar(position = "fill")+
  theme_minimal()
# Notches are used to compare groups; if the notches of two boxes do not overlap, this is a strong evidence that the medians differ.
education_graph

```
# EducationField Graph
```{r}
library(ggplot2)
educationfield_graph = ggplot(data=dataset, aes(x=EducationField,  fill=Attrition))+
  geom_bar(position = "fill")+
  theme_minimal()
# Notches are used to compare groups; if the notches of two boxes do not overlap, this is a strong evidence that the medians differ.
educationfield_graph
```
# EnvironmentSatisfaction Graph
```{r}
library(ggplot2)
environmentsatisfaction_graph = ggplot(data=dataset, aes(x=EnvironmentSatisfaction,  fill=Attrition))+
  geom_bar(position = "fill")+
  theme_minimal()
# Notches are used to compare groups; if the notches of two boxes do not overlap, this is a strong evidence that the medians differ.
environmentsatisfaction_graph
```

# DistanceFromHome graph
```{r}
library(ggplot2)
distancefromhome_graph = ggplot(data=dataset, aes(x=Attrition, y=DistanceFromHome, fill=Attrition))+
  geom_boxplot(notch=TRUE, outlier.alpha = 0)+
  theme_minimal()
# Notches are used to compare groups; if the notches of two boxes do not overlap, this is a strong evidence that the medians differ.
distancefromhome_graph

```
# Gender graph
```{r}
library(ggplot2)
gender_graph = ggplot(data=dataset, aes(x=Gender,  fill=Attrition))+
  geom_bar(position = "fill")+
  theme_minimal()
# Notches are used to compare groups; if the notches of two boxes do not overlap, this is a strong evidence that the medians differ.
gender_graph
```
# HourlyRate graph
```{r}
library(ggplot2)
hourlyrate_graph = 

ggplot(data=dataset, aes(x=Attrition, y=HourlyRate, fill=Attrition))+
  geom_boxplot(notch=TRUE, outlier.alpha = 0)+
  theme_minimal()
# Notches are used to compare groups; if the notches of two boxes do not overlap, this is a strong evidence that the medians differ.
hourlyrate_graph
```
# JobInvolvement graph
```{r}
library(ggplot2)
jobinvolvement_graph = ggplot(data=dataset, aes(x=JobInvolvement,  fill=Attrition))+
  geom_bar(position = "fill")+
  theme_minimal()
# Notches are used to compare groups; if the notches of two boxes do not overlap, this is a strong evidence that the medians differ.
jobinvolvement_graph

```
# JobLevel graph
```{r}
library(ggplot2)
joblevel_graph = ggplot(data=dataset, aes(x=JobLevel,  fill=Attrition))+
  geom_bar(position = "fill")+
  theme_minimal()
# Notches are used to compare groups; if the notches of two boxes do not overlap, this is a strong evidence that the medians differ.
joblevel_graph

```
# JobRole graph
```{r}
library(ggplot2)
jobrole_graph = ggplot(data=dataset, aes(x=JobRole,  fill=Attrition))+
  geom_bar(position = "fill")+
  theme_minimal()
# Notches are used to compare groups; if the notches of two boxes do not overlap, this is a strong evidence that the medians differ.
jobrole_graph

```
# JobSatisfaction graph
```{r}
library(ggplot2)
jobsatisfaction_graph = ggplot(data=dataset, aes(x=JobSatisfaction,  fill=Attrition))+
  geom_bar(position = "fill")+
  theme_minimal()
# Notches are used to compare groups; if the notches of two boxes do not overlap, this is a strong evidence that the medians differ.
jobsatisfaction_graph

```
# MaritalStatus graph
```{r}
library(ggplot2)
maritalstatus_graph = ggplot(data=dataset, aes(x=MaritalStatus,  fill=Attrition))+
  geom_bar(position = "fill")+
  theme_minimal()
# Notches are used to compare groups; if the notches of two boxes do not overlap, this is a strong evidence that the medians differ.
maritalstatus_graph

```
# NumCompaniesWorked graph
```{r}
library(ggplot2)
numcompaniesworked_graph = ggplot(data=dataset, aes(x=NumCompaniesWorked,  fill=Attrition))+
  geom_bar(position = "fill")+
  theme_minimal()
# Notches are used to compare groups; if the notches of two boxes do not overlap, this is a strong evidence that the medians differ.
numcompaniesworked_graph

```
# OverTime graph
```{r}
library(ggplot2)
overtime_graph = ggplot(data=dataset, aes(x=OverTime,  fill=Attrition))+
  geom_bar(position = "fill")+
  theme_minimal()
# Notches are used to compare groups; if the notches of two boxes do not overlap, this is a strong evidence that the medians differ.
overtime_graph

```

# PercentSalaryHike graph
```{r}
library(ggplot2)
percentsalaryhike_graph = ggplot(data=dataset, aes(x=PercentSalaryHike,  fill=Attrition))+
  geom_bar(position = "fill")+
  theme_minimal()
# Notches are used to compare groups; if the notches of two boxes do not overlap, this is a strong evidence that the medians differ.
percentsalaryhike_graph

```
# PerformanceRating graph
```{r}
library(ggplot2)
performancerating_graph = ggplot(data=dataset, aes(x=PerformanceRating,  fill=Attrition))+
  geom_bar(position = "fill")+
  theme_minimal()
# Notches are used to compare groups; if the notches of two boxes do not overlap, this is a strong evidence that the medians differ.
performancerating_graph

```
# RealtionshipSatisfaction graph
```{r}
library(ggplot2)
relationshipsatisfaction_graph = ggplot(data=dataset, aes(x=RelationshipSatisfaction,  fill=Attrition))+
  geom_bar(position = "fill")+
  theme_minimal()
# Notches are used to compare groups; if the notches of two boxes do not overlap, this is a strong evidence that the medians differ.
relationshipsatisfaction_graph

```
# StockOptionLevel graph
```{r}
library(ggplot2)
stockoptionlevel_graph = ggplot(data=dataset, aes(x=StockOptionLevel,  fill=Attrition))+
  geom_bar(position = "fill")+
  theme_minimal()
# Notches are used to compare groups; if the notches of two boxes do not overlap, this is a strong evidence that the medians differ.
stockoptionlevel_graph

```
# TotalWorkingYears graph
```{r}
library(ggplot2)
totalworkingyears_graph = 

ggplot(data=dataset, aes(x=Attrition, y=TotalWorkingYears, fill=Attrition))+
  geom_boxplot(notch=TRUE, outlier.alpha = 0)+
  theme_minimal()
# Notches are used to compare groups; if the notches of two boxes do not overlap, this is a strong evidence that the medians differ.
totalworkingyears_graph

```
# TrainingTimesLastYear graph
```{r}
library(ggplot2)
trainingtimeslastyear_graph = ggplot(data=dataset, aes(x=TrainingTimesLastYear,  fill=Attrition))+
  geom_bar(position = "fill")+
  theme_minimal()
# Notches are used to compare groups; if the notches of two boxes do not overlap, this is a strong evidence that the medians differ.
trainingtimeslastyear_graph

```
# WorkLifeBalance graph
```{r}
library(ggplot2)
worklifebalance_graph = ggplot(data=dataset, aes(x=WorkLifeBalance,  fill=Attrition))+
  geom_bar(position = "fill")+
  theme_minimal()
# Notches are used to compare groups; if the notches of two boxes do not overlap, this is a strong evidence that the medians differ.
worklifebalance_graph

```
# YearsAtCompany graph ~ categories
```{r}
library(ggplot2)
yearsatcompany_categories_graph = ggplot(data=dataset, aes(x=YearsAtCompany,  fill=Attrition))+
  geom_bar(position = "fill")+
  theme_minimal()
# Notches are used to compare groups; if the notches of two boxes do not overlap, this is a strong evidence that the medians differ.
yearsatcompany_categories_graph

```
# YearsAtCompany graph ~ continuous, boxplots
```{r}
library(ggplot2)
totalworkingyears_continuous_graph = 

ggplot(data=dataset, aes(x=Attrition, y=YearsAtCompany, fill=Attrition))+
  geom_boxplot(notch=TRUE, outlier.alpha = 0)+
  theme_minimal()
# Notches are used to compare groups; if the notches of two boxes do not overlap, this is a strong evidence that the medians differ.
totalworkingyears_continuous_graph

```
# YearsInCurrentRole graph
```{r}
library(ggplot2)
yearsincurrentrole_graph = 

ggplot(data=dataset, aes(x=Attrition, y=YearsInCurrentRole, fill=Attrition))+
  geom_boxplot(notch=TRUE, outlier.alpha = 0)+
  theme_minimal()
# Notches are used to compare groups; if the notches of two boxes do not overlap, this is a strong evidence that the medians differ.
yearsincurrentrole_graph

```
# YearsSinceLastPromotion graph
```{r}
library(ggplot2)
yearssincelastpromotion_graph = 

ggplot(data=dataset, aes(x=Attrition, y=YearsSinceLastPromotion, fill=Attrition))+
  geom_boxplot(notch=TRUE, outlier.alpha = 0)+
  theme_minimal()
# Notches are used to compare groups; if the notches of two boxes do not overlap, this is a strong evidence that the medians differ.
yearssincelastpromotion_graph

```
# YearsSinceCurrentManager graph
```{r}
library(ggplot2)
yearswithcurrmanager_graph = 

ggplot(data=dataset, aes(x=Attrition, y=YearsWithCurrManager, fill=Attrition))+
  geom_boxplot(notch=TRUE, outlier.alpha = 0)+
  theme_minimal()
# Notches are used to compare groups; if the notches of two boxes do not overlap, this is a strong evidence that the medians differ.
yearswithcurrmanager_graph

```
```{r}
library(gridExtra)

grid.arrange(businesstravel_graph, department_graph, nrow=2)
```



